---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css echo=FALSE}
body{
    background-color: #feffe4;
}
h2{
  color: red
}
h3{
  color: #3200ff
}
p{
  font-family: Georgia;
  color: #003360;
}
```

## About the data

### Sample size

The sheet contains two types of data, and this is a bar chart showing sample size.

```{r}
library(tidyverse)

logged_data <- read_csv('https://docs.google.com/spreadsheets/d/e/2PACX-1vT1s235dHjiX2r7mUTbtlDm5H_-evr2XGAAXOp3RW4p1_vHsQ5-TG258yudTTZmQxJhnr-7UtrVp3ge/pub?output=csv')

latest_data <- logged_data %>%
  rename(Type = 2,
         Views = 3,
         Likes = 4,
         Author = 5,
         Subscribers = 6,
         Date = 7,
         Title = 8)

# Which one gets higher number of samples?
latest_data %>%
  ggplot() +
    geom_bar(aes(x = Type)) +
  labs(title = "Videos/shorts on YouTube trending",
       subtitle = "Comparing numbers of two types of vedios",
       caption = "Source: YouTube")

paste("With", 
      length(latest_data$Type), 
      "Samples")

```

### Mean of views/subscribers/likes

```{r}
library(tidyverse)

logged_data <- read_csv('https://docs.google.com/spreadsheets/d/e/2PACX-1vT1s235dHjiX2r7mUTbtlDm5H_-evr2XGAAXOp3RW4p1_vHsQ5-TG258yudTTZmQxJhnr-7UtrVp3ge/pub?output=csv')

latest_data <- logged_data %>%
  rename(Type = 2,
         Views = 3,
         Likes = 4,
         Author = 5,
         Subscribers = 6,
         Date = 7,
         Title = 8)

paste("The mean views of",
      length(latest_data$Type),
      "samples is",
      mean(latest_data$Views)%>%round(0))

paste("The mean subscribers of",
      length(latest_data$Type),
      "samples is",
      mean(latest_data$Subscribers)%>%round(0))

paste("The mean likes of",
      length(latest_data$Type),
      "samples is",
      mean(latest_data$Likes)%>%round(0))

```

We can see that there is a big difference between the average of likes and the other values, which may indicate that likes reflect the approval of its content.
Maybe we can create another variable to define the likes rate of each video/short.

```{r}
library(tidyverse)

logged_data <- read_csv('https://docs.google.com/spreadsheets/d/e/2PACX-1vT1s235dHjiX2r7mUTbtlDm5H_-evr2XGAAXOp3RW4p1_vHsQ5-TG258yudTTZmQxJhnr-7UtrVp3ge/pub?output=csv')

latest_data <- logged_data %>%
  rename(Type = 2,
         Views = 3,
         Likes = 4,
         Author = 5,
         Subscribers = 6,
         Date = 7,
         Title = 8)

# To figure out the likes rate
likes_rate <- (latest_data$Likes/latest_data$Views) %>% round(4)

paste("The mean likes rate of",
      length(latest_data$Type),
      "samples is",
      mean(likes_rate) %>% round(4))

# Which one gets higher likes rate?
latest_data %>%
  ggplot() +
    geom_bar(aes(x = likes_rate, fill = Type)) +
  labs(title = "Which one gets higher likes rate?",
       subtitle = "Comparing numbers of likes rate with two types of videos",
       caption = "Source: YouTube",
       x = "Likes rate",
       y = "Number of videos/shorts")

```

From the bar chart above, we can see that shorts gets higher likes rate than videos.

## Furthermore

### Is there a relation between views/subscribers and like rate?

```{r show_col_types = FALSE}
library(tidyverse)

logged_data <- read_csv('https://docs.google.com/spreadsheets/d/e/2PACX-1vT1s235dHjiX2r7mUTbtlDm5H_-evr2XGAAXOp3RW4p1_vHsQ5-TG258yudTTZmQxJhnr-7UtrVp3ge/pub?output=csv')

latest_data <- logged_data %>%
  rename(Type = 2,
         Views = 3,
         Likes = 4,
         Author = 5,
         Subscribers = 6,
         Date = 7,
         Title = 8)

# To figure out the likes rate
likes_rate <- (latest_data$Likes/latest_data$Views) %>% round(4)

# Higher views means higher likes rate?
latest_data %>%
  ggplot() +
    geom_point(aes(x = Views, y = likes_rate, fill = Type, colour = Type)) +
    geom_smooth(aes(x = Views, y = likes_rate), method = "lm", se = FALSE) +
  labs(title = "Higher views, higher likes rate?",
       subtitle = "Comparing number of views and likes rate with two types of videos",
       caption = "Source: YouTube",
       x = "Number of views",
       y = "Likes rate")

# Higher subscribers means higher likes rate?
latest_data %>%
  ggplot() +
  geom_point(aes(x = Subscribers, y = likes_rate, fill = Type, colour = Type)) +
  geom_smooth(aes(x = Subscribers, y = likes_rate), method = "lm", se = FALSE) +
  labs(title = "Higher subscribers, higher likes rate?",
       subtitle = "Comparing number of subscribers and likes rate with two types of videos",
       caption = "Source: YouTube",
       x = "Number of subscribers",
       y = "Likes rate")

```

From the above scatter plot, we can see that there is a decreased relationship between the number of views and the likes rate, which means the more in views, the lower in likes rate. However, there is no obvious relationship between the number of subscriptions and likes rate.
